---
title       : Slidify
subtitle    : Developing Data Products.
author      : Akhil Kumar Ramasagaram
job         : CS Student, Gitam University.
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction.

- For this project I have used the "mtcars" dataset which can be found in `r library(datasets)`.
- The main goal of this project was that it predicts the optimal miles per gallon(mpg) using two predictor variables.
- The Predictor variables are 'cyl'(number of Cylinders) and 'hp'(horsepower).
- The user can use any one of the predictor or he can use all the variables in his model.
- The predictions are calculated by simple linear regression model.


--- .class #id 

## Regression model.
```{r echo = TRUE}
model = lm(mpg ~ cyl+hp, data = mtcars)
summary(model)
```
--- .class #id 
## Input.
- As we can see from the application running on HTML. There are 2 checkbox's to select the predictor/(s). 
```{r echo=TRUE,eval=FALSE}
checkboxGroupInput("checkbox", label = h3("Select predictor/(s)"),
                            choices = list("Cylinders" = "cyl", "Horsepower" = "hp")),
```
- Just below that we have two numerical input features where a user can set the values with predetermined incremental values. I have set 4 and 50 for cylinders and horsepower respectively as the default value and the incremental value is derived from the step parameter
```{r echo=TRUE,eval=FALSE}
numericInput('cr', 'Number of cylinders', 4, min = 4, max = 8, step = 2),
numericInput('hp', 'Gross horsepower', 50, min = 50, max = 350, step = 5),
```
--- .class #id 
## Output.
- The mainPanal() shows the output for out application.
```{r echo=TRUE,eval=FALSE}
mainPanel(
      h3('Result'),
      h4('Predictor/(s) Selected'),                                             
      verbatimTextOutput("predictors"),                                         
      h4('MODEL'),                                                              
      verbatimTextOutput("model"),                                               
      h4('Predicted MPG'),                                                      
      verbatimTextOutput("prediction")                                          
    )
```


